\textbf{International Transport costs:\\New Findings from modeling additive costs}\\Online Appendix (Not for Publication)

### 2021-07-30 redaction/JEGeo/revision_JEGeo/revised_article/DHP_JoEG_rev1.tex

\begin{table}[htbp]
  \centering
  \caption{Trade liberalization: The role of additive costs} \label{tab:resultats_modele}
\begin{center}
\begin{tabular}{l|c|c|c|c||c|c|c|c}
\hline
Mode & \multicolumn{4}{|c||}{Air} & \multicolumn{4}{c}{Vessel} \\ \hline
Exercise &  \multicolumn{2}{|c|}{Constant $f_x$} &  \multicolumn{2}{|c||}{Lower $f_x$} & \multicolumn{2}{|c|}{Constant $f_x$} &  \multicolumn{2}{|c}{Lower $f_x$} \\ \hline
Reduction in & $\tau$ only & $\tau$ and $t$ &$\tau$ only & $\tau$ and $t$ & $\tau$ only & $\tau$ and $t$ &$\tau$ only & $\tau$ and $t$\\ \hline
$TC_{1974}$ & 0.062 & 0.062 & 0.062 & 0.062 & 0.105 & 0.105 & 0.105 & 0.105\\
$TC_{2019}$ &  0.028 & 0.028 & 0.028 & 0.028&  0.041 & 0.041 & 0.041 & 0.041\\
$\Delta TC$ (in pp) &  -0.034 & -0.034 & -0.034 & -0.034 & -0.064 & -0.064 & -0.064 & -0.064\\
$\Delta \tau$ (in pp) & -0.0340	&-0.0140&	-0.0340&	-0.0140	&-0.064&	-0.031&	-0.064&	-0.031  \\
$\Delta t/\widetilde{p}_x^{\text{fas}}$ (in pp) & 0&	-0.02&	0&	-0.02&	0&	-0.033&	0&	-0.033  \\ \hline
$\Delta \mathcal{U}$ & 0.0202&	0.0295	&0.0362&	0.0527	&0.035&	0.052	&0.047&	0.064 \\
$\Delta \mathcal{U}/\mathcal{U}$ (in \%) & 1.2319&	1.8187&	2.2073	&3.2477	&2.179	&3.295&	2.872&	4.052   \\
\hline
\end{tabular} 
\end{center}
{\parbox[l]{15cm}{ \vspace{4pt}\footnotesize{Notes: TC = Transport Costs, expressed in percentage of the average export fas price.}}}
\end{table}

>>>>

The results are reported in Table \ref{tab:resultats_modele}, for Air (Columns (1)-(4)) and Vessel (Columns (5)-(8)) respectively. Specifically, we report the change in total transport costs (expressed in percentage points, and based on the raw numbers reported in Table \ref{tab:calib_TC}), decomposed in its two dimensions (additive and ad-valorem); as well as the welfare change, both in absolute and in relative terms. For each transport mode, the first two columns report the results of reducing transport costs only, maintaining the same value of $f_x$ as in the initial equilibrium (Columns (1)-(2) for Air, (5)-(6) for Vessel), contrasting the case of only ad-valorem costs (Columns (1), (5)) and in presence of transport costs (Columns (2), (6)). In Columns (3)-(4) for Air and (7)-(8), we report the results when both the variable transport costs and the fixed export costs are lower in the final steady state (2019) relative to the initial one (1974).

\begin{table}[htbp]
  \centering
  \caption{Trade liberalization: The role of additive costs} \label{tab:resultats_modele}
\begin{center}
\begin{tabular}{l|c|c|c|c||c|c|c|c}
\hline
Mode & \multicolumn{4}{|c||}{Air} & \multicolumn{4}{c}{Vessel} \\ \hline
Fixed export cost: &  \multicolumn{2}{|c|}{Constant $f_x$} &  \multicolumn{2}{|c||}{Lower $f_x$} & \multicolumn{2}{|c|}{Constant $f_x$} & \multicolumn{2}{|c}{Lower $f_x$} \\ \hline
Reduction in: & $\tau$ only & $\tau$ and $t$ &$\tau$ only & $\tau$ and $t$ & $\tau$ only & $\tau$ and $t$ &$\tau$ only & $\tau$ and $t$\\ \hline
%$TC_{1974}$ & 0.062 & 0.062 & 0.062 & 0.062 & 0.105 & 0.105 & 0.105 & 0.105\\
%$TC_{2019}$ &  0.028 & 0.028 & 0.028 & 0.028&  0.041 & 0.041 & 0.041 & 0.041\\
$\Delta TC$ (in pp) &-3.4 &-3.4 &-3.4 &-3.4 &-6.4 &-6.4 &-6.4 &-6.4  \\ 
$\Delta \tau$ (in pp) & -3.4	&-1.4&	-3.40&	-1.40	&-6.4&	-3.1&	-6.4&	-3.1  \\ 
$\Delta t/\widetilde{p}_x^{\text{fas}}$ (in pp) & 0&	-2.0&	0&	-2.0&	0&	-3.3&	0&	-3.3  \\ \hline
$\Delta \mathcal{U}$ & 0.0202&	0.0295	&0.0362&	0.0527	&0.035&	0.052	&0.047&	0.064 \\
$\Delta \mathcal{U}/\mathcal{U}$ (in \%) & 1.2319&	1.8187&	2.2073	&3.2477	&2.179	&3.295&	2.872&	4.052   \\
\hline
\end{tabular}
\end{center}
{\parbox[l]{15cm}{ \vspace{4pt}\footnotesize{Notes: TC = Transport Costs. The reduction in transport costs is expressed in percentage points. }}}
\end{table}

\subsubsection{Reducing international transport costs}

In this first exercise, we contrast the effects of a reduction of international transport costs depending on whether this occurs through a reduction in ad-valorem costs only, or a combined reduction in both the additive and the multiplicative components. Accordingly, we focus on the results reported in Table \ref{tab:resultats_modele}, Column (1) versus (2) for Air, Column (5) versus (6) for Vessel.

A first conclusion emerges: Whatever the transport mode (and the magnitude of the transport costs decrease accordingly), welfare gains are higher when this reduction is made (partly) through a reduction of additive costs. The effect is substantial: In Air transport, the reduction of 3.4 percentage points of transport costs generates a welfare gain higher by 0.58 percentage point when almost 60\% of such a reduction occurs through the additive component, rather than when it realizes through a decrease of iceberg costs only. In maritime transport, where the decrease in total transport costs is larger (by 6.4 percentage points), the extra welfare gain amounts to 1.12 percentage points when 50\% of the transport cost reduction occurs through the additive component.

### 2021-07-30 redaction/JEGeo/revision_JEGeo/revised_article/donnees_calibration.tex

\begin{tabular}{lll}
& Value & Reference\\
\hline
sigma & 4 & \cite{Irrazabal_2015}\\
fe & 1 & \cite{ghironi}\\
f & 0.033333 & Share of exporters = 21\% (\cite{ghironi}) \\
L & 1 & Arbitrary\\
$\delta$ & 0.1 & \cite{ghironi}, \cite{Irrazabal_2015}\\
k & 4 \\
$\varphi_{\text{min}}$ & 1 & \cite{ghironi}, \cite{Irrazabal_2015}\\
\hline
\end{tabular}

>>>>

\begin{tabular}{lll}
& Value & Reference\\
\hline
$\sigma$ & 4 & \cite{Irrazabal_2015}\\
$f_e$ & 1 & \cite{ghironi}\\
$f$ & 0.033 & \cite{ghironi} \\
$f_x$ & 0.09 & Share of exporters = 21\% (\cite{ghironi}, \cite{Irrazabal_2015}) \\
$L$ & 1 & Arbitrary\\
$\delta$ & 0.1 & \cite{ghironi}, \cite{Irrazabal_2015}\\
$k$ & 4 \\
$\varphi_{\text{min}}$ & 1 & \cite{ghironi}, \cite{Irrazabal_2015}\\
\hline
\end{tabular}
